Graph-Based Neural Reconstruction from Skeletonized 3D Networks

### 2018-03-11 papers/eccv2018/2_method.tex
eccv2018: updated figures

\begin{figure}[t]
	\centering
	\includegraphics[width=0.32\linewidth]{./figures/skeleton1.png}
	\includegraphics[width=0.32\linewidth]{./figures/skeleton2.png}
	\includegraphics[width=0.32\linewidth]{./figures/skeleton3.png}
	\caption{Example skeletons (in black) extracted from segments using a variant of the TEASER algorithm.}
	\label{fig:skeletonization}
\end{figure}

@@

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[width=0.45\linewidth]{./figures/skeleton1.png}
	\includegraphics[width=0.45\linewidth]{./figures/skeleton2.png}
	\includegraphics[width=0.45\linewidth]{./figures/skeleton3.png}
	\includegraphics[width=0.45\linewidth]{./figures/skeleton4.png}
	\caption{Example skeletons (in black) extracted from segments using a variant of the TEASER algorithm.}
	\label{fig:skeletonization}
\end{figure}

@@

\paragraph{Post-processing}

By reformulating the segmentation problem as a graph partitioning one, we can enforce some global constraints on our result based on the underlying biology.
Traditional hierarchical clustering algorithms do not rely on such constraints but consider local decisions independently.
The multicut problems returns a series of ``collapsed'' edges between nodes that belong to the same neuron.
We iterate over these edges in order of the probability of merge generated by our CNN. 
\TODO{HOW DO WE ACCOMPLISH THIS}
